---
title: "Using Petfindr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using Petfindr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of 'PetFindr' is to provide a fast and friendly way to extract data from https://www.petfinder.com/, which is the largest online pet adoption website, and to facilitate data analysis and other tasks from the extracted data.\

The package provides a useful tool to enable R users to search for their favorite pets in their own R session, and to browse pictures of the pets. All of this is possible thanks to API (Application Programming Interface) which is a set of instructions and standards for accessing structured information on the web. The Petfinder website provides us with an API that allows us to access the Petfinder database of hundreds of thousands of pets ready for adoption and over ten thousand animal welfare organizations. \

This vignette introduces and walks through the package,`PetFindr`, and the Petfinder API for authenticating and extracting data from the database.\


### Getting Started

First, you need to install and load the `PetFindr` package.


```{r setup}
library(PetFindr)
```



To get your own `key` and `secret` from the API website, you have to create an account on [Petfinder](https://www.petfinder.com/user/register/).\

`pf_setup` function will guide you through whole process to initialize the API connection to Petfinder.\
Running this function will open a browser to "https://www.petfinder.com/developers/" and prompt you to register for Petfinder's API (V2).

```{r}
pf_setup()

```




```{r}
#1: No way
#2: Not now
#3: Yup

```


```{r, eval = F}
pf_save_credentials(key, secret)
````
Once you creat an account on [Petfinder](https://www.petfinder.com/) and receive a unique `key` and a secret, you now can use the function `petfindr_save_credentials()` to store their key and secret to your .Rprofile so that you do not have to run `pf_save_credentials(key, secret)` everytime you use the package. /









